Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-04-15 paper/abstraction/paper.tex
more spelling fixes from aspell

As described earlier (\S\ref{sec:introduction}), templates are hard to author and hard to validate. Worse, templates that work for one topology may not work for seemingly-inconsequential variations which may arise after the network evolves.
Consider the network in Figure~\ref{fig:example2}, which is similar to Figure~\ref{fig:example}; it has the same five roles, connected in a similar hierarchy. One might think that the same templates, with different database entries, can be used for both cases. However, if the templates are configured to disallow ``valley" paths (per policy (5) above), they will work for Figure~\ref{fig:example} but silently violate the fault tolerance policy $(8)$ when used for Figure~\ref{fig:example2}.  Specifically, in Figure~\ref{fig:example2}, an aggregation-based black hole (\S\ref{sec:background}) will occur when the link S1--A1 fails; after this failure, S1 has no valley-free path to P[1--2] even though it will continue to get traffic for these prefixes as it announces the covering prefix PG (because it gets routes for P[3--4]). Such a black hole will not occur in Figure~\ref{fig:example} because spine routers have two links to each pod.

@@

On its own, this abstraction loses a lot of information about the concrete network's structure, making it difficult to reason precisely about fault-tolerance.
For example, with this abstraction any spine router may or may not connect to any aggregator router.
%
To capture concrete networks more precisely,
we introduce additional concepts. The first is topology hierarchy, captured by P and Q, which indicate that nodes in the ToR and aggregator roles are grouped into pods.
The second is node and edge \emph{multiplicity}. Each edge (and node) is labelled
with a symbolic variable (\EG, $e1$) that denotes a constraint on the number of edges (and nodes) that may appear in any valid concrete network. Operators can capture concrete network invariants by adding constraints on the symbolic variables using logical formulas.

@@

\begin{defn}
Let $m \geq_{rank} n$ be a relation over PG vertices that holds iff $\Topo{m} = \Topo{n}$ and either $\min (\Pref(m)) \geq \min (\Pref(n))$ or $\Pref(n) = \emptyset$.
%
\end{defn}
\noindent
%
Intuitively $m \geq_{rank} n$ means that paths ending at node $n$ have lower automata rank and are thus better than paths ending at $m$.
%\begin{defn}
The PG can be viewed as a labelled transition system by pushing the location from each directed edge's target node onto the edge. That is, $m\overset{l}{\rightarrow}n$ if there is an edge $(m,n)$ in the PG and $\Topo{n} = l$.
%\end{defn}
%
For example, in the concrete PG we have the transition $(S1,1,0)\overset{A2}{\rightarrow}(A2,1,0)$.

>>>>

As described earlier (\S\ref{sec:introduction}), templates are hard to author and hard to validate. Worse, templates that work for one topology may not work for seemingly-inconsequential variations which may arise after the network evolves.
Consider the network in Figure~\ref{fig:example2}, which is similar to Figure~\ref{fig:example}; it has the same five roles, connected in a similar hierarchy. One might think that the same templates, with different database entries, can be used for both cases. However, if the templates are configured to disallow ``valley" paths (per policy (5) above), they will work for Figure~\ref{fig:example} but silently violate the fault tolerance policy $(8)$ when used for Figure~\ref{fig:example2}.  Specifically, in Figure~\ref{fig:example2}, an aggregation-based black hole (\S\ref{sec:background}) will occur when the link S1--A1 fails; after this failure, S1 has no valley-free path to P[1--2] even though it will continue to get traffic for these prefixes as it announces the covering prefix PG (because it gets routes for P[3--4]). Such a black hole will not occur in Fn Figure~\ref{fig:example} because spine routers have two links to each pod.

@@

On its own, this abstraction loses a lot of information about the concrete network's structure, making it difficult to reason precisely about fault-tolerance.
For example, with this abstraction any spine router may or may not connect to any aggregator router.
%
To capture concrete networks more precisely,
we introduce additional concepts. The first is topology hierarchy, captured by P and Q, which indicate that nodes in the ToR and aggregator roles are grouped into pods.
The second is node and edge \emph{multiplicity}. Each edge (and node) is labeled
with a symbolic variable (\EG, $e1$) that denotes a constraint on the number of edges (and nodes) that may appear in any valid concrete network. Operators can capture concrete network invariants by adding constraints on the symbolic variables using logical formulas.

@@

\begin{defn}
Let $m \geq_{rank} n$ be a relation over PG vertices that holds iff $\Topo{m} = \Topo{n}$ and either $\min (\Pref(m)) \geq \min (\Pref(n))$ or $\Pref(n) = \emptyset$.
%
\end{defn}
\noindent
%
Intuitively $m \geq_{rank} n$ means that paths ending at node $n$ have lower automata rank and are thus better than paths ending at $m$.
%\begin{defn}
The PG can be viewed as a labeled transition system by pushing the location from each directed edge's target node onto the edge. That is, $m\overset{l}{\rightarrow}n$ if there is an edge $(m,n)$ in the PG and $\Topo{n} = l$.
%\end{defn}
%
For example, in the concrete PG we have the transition $(S1,1,0)\overset{A2}{\rightarrow}(A2,1,0)$.
